Clustering: A pipeline to analyse time-course gene expression data

### 2019-05-01 scripts/03_clustering.Rmd
Disabling test to cache packages

The next step is to perform clustering. First, we reduce the set of genes of
interest to genes that are (1) significant; (2) "highly" differentially
expressed. First, we select the genes that have a log-fold change of at least
2 across at least one experiment for one time point. We thus use the object
`lfc_max`.

XXX

@@

```{r clustering}

#############################################################################
# Fit the splines

kmeans_clusters = moanin:::splines_kmeans(
    y, splines_model, n_clusters=20,
    random_seed=42,
    n_init=20)

all_scores = matrix(NA, nrow=dim(data)[1], ncol=n_clusters)

for(k in 1:n_clusters){
     scores = moanin:::score_genes_centroid(
	data,
	kmeans_clusters$centroids[k,])
     all_scores[, k] = scores
}

all_scores = as.matrix(all_scores)
# Only assign labels to X% of the genes
max_score = quantile(rowMin(all_scores), c(percentage_genes_to_label))
genes_to_not_consider = rowMin(all_scores) >= max_score
labels = apply(all_scores, 1, which.min)
labels[genes_to_not_consider] = NA
names(labels) = row.names(data)
```

@@

```{r}
barplot(table(labels), col="black")
labels = kmeans_clusters$clusters
```

>>>>

The next step is to perform clustering. First, we reduce the set of genes of
interest to genes that are (1) significant; (2) "highly" differentially
expressed. First, we select the genes that have a log-fold change of at least
2 across at least one experiment for one time point.

@@

```{r clustering}
# First fit the kmeans clusters
kmeans_clusters = moanin:::splines_kmeans(
    y, splines_model, n_clusters=20,
    random_seed=42,
    n_init=20)

# Then assign scores and labels to all the data, using a goodness-of-fit
# scoring function.
scores_and_labels = moanin::splines_kmeans_score_and_label(
    data, kmeans_clusters)
labels = scores_and_labels$labels
```

@@

```{r}
barplot(table(labels), col="black")
```
